
\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}
\usepackage{ragged2e}
\usepackage{float}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}   
\usepackage[english]{babel}
\moderncvstyle{classic}                            
% Page margins
\usepackage[scale=0.8]{geometry} % Page margins

% Your Information, please revise
\name{Sammy}{Robens-Paradise}
\address{323 East 18th Ave.}{Vancouver, BC V5V 1E7}
 
\begin{document}
\\
\newline
\\
\recipient{Chair of Department, \\
Department of Systems Design Engineering \newline\\
Dear Dr. Aultman-Hall,}{}
\makelettertitle
\justifying
\indent
I have prepared this report, “A Comparison of Software Source Code Control Systems in Modern Software Development” as my 2B Work Report. This report is the first of three that I must submit as part of my degree requirements. It was entirely written by me and has not received any previous academic credit at this or any other institution. This report was written after my 2A term of Systems Design Engineering. It investigates whether a migration from a centralized version control system to a distributed version control system qualitatively and quantitatively resulted in a more efficient software development life-cycle, from the standpoint of a software development team at an upstart Software-As-A-Service company based in Vancouver, British Columbia. This report was inspired by my immediate Supervisor, Rob Kraft, MASc. President of PUMA who asked me to discover and implement software development practices optimizing the development life cycle. This inspired me to investigate the relationship between centralized, and decentralized version control systems and their influence on the software development life-cycle. I would like to thank Rob Kraft, P. Eng., MASc. President of PUMA, Elina Poversky, Sr. Computer Scientist at PUMA and Stephen Leong, Developer at Bayleaf Software for their mentor-ship and participation in this report. \\

\\
Sammy Robens-Paradise, ID: 20709541, Systems Design Engineering

\vspace{0.5cm}

\end{document}